---
title: "BigMac"
author: "Jaime Duran"
date: "March 25, 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
Get an estimated demand curve for Big Macs. Try to get elasticity demand

```{r}
BigMacdata = read.csv('Big Mac Price and Purchases.csv') 
attach(BigMacdata)
```

plot the data 

```{r}
plot(demand~price)

```

fit demand line to these data

```{r}
priceOne = 4.00
model1 = lm(demand~price)
#summary(model1)
plot(demand~price)
abline(h = 2, col= "red")
abline(model1)

```

price elasticity is the % change in quantity demanded divided by the % change in price 

marginal revenue is the additional revenue earned by selling one more unit of that product

MR = price * (1+elasticity)/elasticity

Elasticity = E

E = slope of demand at price P * (price/quantity)

```{r}
slope = model1$coefficients[2]
intercept = model1$coefficients[1]
demanded = (priceOne-intercept)/slope

E = slope*priceOne/demanded

MR = priceOne * abs((1+E)/E)
print(paste('elasticity = ', round(E,2)))
print(paste('MR = ', round(MR,2)))

```

Profit = price - cost = 4.0 - MC
```{r}
profit = priceOne - MR
print(paste('profit = ', profit))

```

## Solution
Estimated Demand Curve for Big Macs
- This graph demonstrates price points on the x axis and the demand for Big Macs per customer is represented by along the y axis. 

```{r}
priceOne = 4.00
model1 = lm(demand~price)
#summary(model1)
plot(demand~price)
abline(h = 2, col= "red")
abline(model1)
```


The Elasticity Demand for Big Macs is -0.67, which means that for each increment in price by a full dollar, you could expect to sell 67% less Big Macs. Since the Marginal Revenue for selling one more big mac is 1.98, it may be most convinient to sell each Big Mac for 6 or 7 dollars to satisfy demand while controlling the amount of outgoing product. The range between 5 and 8 dollars represents the price at which customers would buy more than one Big Mac for the highest price.


```{r}
slope = model1$coefficients[2]
intercept = model1$coefficients[1]
demanded = (priceOne-intercept)/slope

E = slope*priceOne/demanded

MR = priceOne * abs((1+E)/E)
print(paste('elasticity = ', round(E,2)))
print(paste('MR = ', round(MR,2)))
```


